### 2010-12-29 docs/slides/application.tex
Analysis and application updated.

\frame
{
	\frametitle{Application}
}

>>>>

\frame
{
	\frametitle{Future Work:}
	\framesubtitle{Application}

	\begin{itemize}
		\item \textbf{Goal:} Apply evolution of mimicry to solve a problem in Computer Science.
		\item Challenges for applying to optimization problem:
			\begin{itemize}
				\item Associating palatability with CA pattern.
				\item Solution set: 2D CA pattern among which the prey species vary.
				\item Palatability is equivalent to evaluation/fitness function.
				\item Then why have mimics in the solution set, when mimics will have the same pattern as the model.
			\end{itemize}
		\item Conclusion: solving optimization problem is futile.
		\item Apply evolution of mimicry to a problem where \textit{deception} is useful.
	\end{itemize}
}

\frame
{
	\frametitle{Deception}
	\framesubtitle{Anti-Virus vs. Virus scenario}

	\begin{itemize}
		\item Anti-Virus \(\leftrightarrow\) Predator
		\item Program (virus free) \(\leftrightarrow\) Prey (model, unpalatable)
		\item Virus \(\leftrightarrow\) Prey (mimic, palatable)
	\end{itemize}

	\begin{itemize}
		\item Objective of a virus is to \textit{mimic} a normal program to get pass an anti-virus software.
		\item Objective is \textbf{malicious}.
	\end{itemize}
}
